On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-08-23 paper.tex
Minor changes in tex file

\newcommand{\mr}{\mathrm}
\newcommand{\st}{\mid}%{\,|\,}
\newcommand{\cond}{\,|\,} % less spacing that \mid
\newcommand{\diff}{\,\mathrm d}
\let\Re\relax % remove the command...
\DeclareMathOperator{\Re}{Re} % ...to define it differently
\let\Im\relax
\DeclareMathOperator{\Im}{Im}
\DeclareMathOperator{\E}{E}
\newcommand{\funt}{\tau} % function that gives maximum number of touched tiles for real-valued length
\newcommand{\funl}{\lambda} % function that gives infimum real-valued length for a given number of touched tiles
\newcommand{\funti}{T} % function that gives maximum number of touched tiles for integer-valued length
\newcommand{\funli}{\Lambda} % function that gives minimum integer-valued length for a given number of touched tiles
\newcommand{\funta}{\varphi} % function that gives average number of touched tiles for real-valued length
\newcommand{\probmax}{\zeta} % function that gives the probability of achieving the maximum number of touched files in the square case for real-valued length
\newcommand{\len}{\ell} % length variable, real-valued
\newcommand{\leni}{\ell} % length variable, integer-valued. Same notation, but I keep the different command just in case
\newcommand{\tiles}{t} % number of tiles (integer-valued)
\newcommand{\isolr}{i^+}
\newcommand{\jsolr}{j^+}
\newcommand{\isoli}{i^\ast}
\newcommand{\jsoli}{j^\ast}
\newcommand{\genfun}{q}
\newcommand{\genvar}{r}
\newcommand{\mss}{M}

@@

\begin{figure}%
\centering%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_inverse}%
\caption{Obtaining $(\isoli,\jsoli)$ in Proposition~\ref{prop: min suff set, form}. Example with $a=1.35, b=1$.%
}%
\label{fig: ijLS_1p35_detail_inverse}%
\end{figure}%
\end{proof}

@@

\begin{figure}
\centering%
\subfigure[$\len = 3.1$: $(\isoli,\jsoli) \in \mss$]{%
\label{fig: ijLS_1p35_detail_in}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_in}%
}\\%\hfill%
\subfigure[$\len = 3.7$: $(\isoli,\jsoli) \notin \mss$]{%
\label{fig: ijLS_1p35_detail_notin}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_notin}%
}%
\caption{Obtaining $(\isoli,\jsoli)$ in Theorem~\ref{theo: funt, form}. Examples with $a=1.35, b=1$.
}%
\label{fig: ijLS_1p35_detail}%
\end{figure}%

@@

From Theorem~\ref{theo: funt, sq, form} it is easily seen that odd values of $\funt(\len)$ correspond to $\isoli = \jsoli$, whereas even values are achieved with $\jsoli = \isoli+1$. Given $\tiles \geq 3$ with $t$ odd, $\funt(\len) = \tiles$ if and only
\begin{equation}
\label{eq: square, odd max tiles, lengths}
\frac \len a \in \left( \frac{\tiles-3}{\sqrt{2}}, \frac{ \sqrt{(\tiles-1)^2+(\tiles-3)^2}}{2} \right].
\end{equation}
For $\tiles \geq 3$, $t$ even, $\funt(\len) = \tiles$ if and only if
\begin{equation}
\label{eq: square, even max tiles, lengths}
\frac \len a \in \left(\frac{ \sqrt{(\tiles-2)^2+(\tiles-4)^2}}{2}, \frac{\tiles-2}{\sqrt{2}} \right].
\end{equation}

>>>>

\newcommand{\mr}{\mathrm}
\newcommand{\st}{\mid}%{\,|\,}
\newcommand{\cond}{\,|\,} % less spacing that \mid
\newcommand{\diff}{\,\mathrm d}
\let\Re\relax % remove the command...
\DeclareMathOperator{\Re}{Re} % ...to define it differently
\let\Im\relax
\DeclareMathOperator{\Im}{Im}
\DeclareMathOperator{\E}{E}
\newcommand{\funt}{\tau} % function that gives maximum number of touched tiles for real-valued length
\newcommand{\funl}{\lambda} % function that gives infimum real-valued length for a given number of touched tiles
\newcommand{\funti}{T} % function that gives maximum number of touched tiles for integer-valued length
\newcommand{\funli}{\Lambda} % function that gives minimum integer-valued length for a given number of touched tiles
\newcommand{\funta}{\varphi} % function that gives average number of touched tiles for real-valued length
\newcommand{\probmax}{\rho} % function that gives the probability of achieving the maximum number of touched files in the square case for real-valued length
\newcommand{\len}{\ell} % length variable, real-valued
\newcommand{\leni}{\ell} % length variable, integer-valued. Same notation, but I keep the different command just in case
\newcommand{\tiles}{t} % number of tiles (integer-valued)
\newcommand{\isolr}{i^+}
\newcommand{\jsolr}{j^+}
\newcommand{\isoli}{i^\ast}
\newcommand{\jsoli}{j^\ast}
\newcommand{\genfun}{q}
\newcommand{\genvar}{r}
\newcommand{\mss}{M}

@@

\begin{figure}%
\centering%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_inverse}%
\caption{Obtaining $(\isoli,\jsoli)$ in Proposition~\ref{prop: min suff set, form}. Example with $a=1.35, b=1$%
}%
\label{fig: ijLS_1p35_detail_inverse}%
\end{figure}%
\end{proof}

@@

\begin{figure}
\centering%
\subfigure[$\len = 3.1$: $(\isoli,\jsoli) \in \mss$]{%
\label{fig: ijLS_1p35_detail_in}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_in}%
}\\%\hfill%
\subfigure[$\len = 3.7$: $(\isoli,\jsoli) \notin \mss$]{%
\label{fig: ijLS_1p35_detail_notin}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_notin}%
}%
\caption{Obtaining $(\isoli,\jsoli)$ in Theorem~\ref{theo: funt, form}. Examples with $a=1.35, b=1$%
}%
\label{fig: ijLS_1p35_detail}%
\end{figure}%

@@

From Theorem~\ref{theo: funt, sq, form} it is easily seen that odd values of $\funt(\len)$ correspond to $\isoli = \jsoli$, whereas even values are achieved with $\jsoli = \isoli+1$. Given $\tiles \geq 3$ with $t$ odd, $\funt(\len) = \tiles$ if and only
\begin{equation}
\label{eq: square, odd max tiles, lengths}
\frac \len a \in \left( \frac{\tiles-3}{\sqrt{2}}, \frac{ \sqrt{(\tiles-1)^2+(\tiles-3)^2}}{2} \right].
\end{equation}
For $\tiles \geq 4$, $t$ even, $\funt(\len) = \tiles$ if and only if
\begin{equation}
\label{eq: square, even max tiles, lengths}
\frac \len a \in \left(\frac{ \sqrt{(\tiles-2)^2+(\tiles-4)^2}}{2}, \frac{\tiles-2}{\sqrt{2}} \right].
\end{equation}
